---
title: "DV (4) HW"
author: Carter Wyatt
format: html
editor: visual
embed resources: true
---

## Question 1

```{r}
library(tidyverse)

# Read in the data 
tv_ratings <- read_csv("https://raw.githubusercontent.com/vaiseys/dav-course/main/Data/tv_ratings.csv")

# Glimpse the data 
glimpse(tv_ratings)
```

```{r}
tv_long <- tv_ratings %>% 
  group_by(title) %>% 
  summarise(num_seasons = n()) %>% 
  ungroup() %>% 
  left_join(tv_ratings, by = "title") 

tv_long <- tv_long %>% 
  filter(num_seasons >= 5)
```

Use `tv_long` to make a line plot to trace how average ratings evolve across seasons. Remember to use the group aesthetic so that each line represents one show.

```{r}
tv_long |>
  ggplot(data = tv_long, mapping = aes(x = seasonNumber, y = av_rating, group = titleId)) + 
geom_line() +
  labs( x = "Seasons", y = "Average Ratings", title = "How Average Ratings Evolve Across Seasons")
```

It should look fairly messy. Can you draw any conclusions from it?

The only conclusions that I can draw is the average ratings seem to dip fairly low every five years and they are rising back to the top by season twenty.

## Question 2

```{r}
tv_long |>
  ggplot(data = tv_long, mapping = aes(x = seasonNumber, y = av_rating, group = titleId)) + 
geom_line() +
  labs( x = "Seasons", y = "Average Ratings", title = "How Average Ratings Evolve Across Seasons") +
  facet_wrap(~genres)
```

What shows tend to last longer?

It seems that crime, drama, and mystery seem to last as they span across the most amount of seasons.

Do ratings change much across seasons?

Ratings do change very much across seasons, the line is up and down continuously on the graph.

Can you identify that show on `Drama, Family, Fantasy` whose ratings just plummeted?

The show "Are You Afraid of the Dark?" caused the ratings to plummet.

## Question 3

```{r}
 tv_ratings |> 
  group_by(genres) |> 
  filter(av_rating >= 9) |> 
  ggplot(aes(x = genres)) +
  geom_bar() +
   coord_flip() +
   labs(x = "Rating Count", y = "Genres", title = "Movie Genre Ratings")

```

Tell me what `coord_flip()` does?

The function "coord_flip", completely flips the x and y variable so it is easier to read on the graph.

What is the genre with the most top-rated shows?

Drama is by far the genre with the most top-rated shows.

## Question 4

```{r}
comedies_dramas <- tv_ratings %>% 
  mutate(is_comedy = if_else(str_detect(genres, "Comedy"), 
                             1, 
                             0)) %>% # If it contains the word comedy then 1, else 0
  filter(is_comedy == 1 | genres == "Drama") %>% # Keep comedies and dramas
  mutate(genres = if_else(genres == "Drama", # Make it so that we only have those two genres
                          "Drama", 
                          "Comedy"))

glimpse(comedies_dramas) |>
  ggplot(aes(x = av_rating, group = genres, color = genres)) +
  geom_density() +
  labs(x = "Average Ratings", y = "Density", title = "Comedy vs. Drama")
```

How does my prediction above hold? Are dramas rated higher?

Your predictions above do hold true as comedies do rival the best dramas, and comedies are actually rated higher.

## Question 5

Let's experiment with different ways of visualizing this. First, do the same plot using histograms.

```{r}
comedies_dramas <- tv_ratings %>% 
  mutate(is_comedy = if_else(str_detect(genres, "Comedy"), 
                             1, 
                             0)) %>% # If it contains the word comedy then 1, else 0
  filter(is_comedy == 1 | genres == "Drama") %>% # Keep comedies and dramas
  mutate(genres = if_else(genres == "Drama", # Make it so that we only have those two genres
                          "Drama", 
                          "Comedy"))

glimpse(comedies_dramas) |>
  ggplot(aes(x = av_rating, group = genres, color = genres)) +
  geom_histogram() +
  labs(x = "Average Ratings", y = "Density", title = "Comedy vs. Drama")
```

What additional information does this give you?

The histogram gives one the ability to tell the density of each genres average rating.

Now, use `geom_freqpoly()`. What do you notice? Of the three plots, which one do you think it's more informative?

```{r}
comedies_dramas <- tv_ratings %>% 
  mutate(is_comedy = if_else(str_detect(genres, "Comedy"), 
                             1, 
                             0)) %>% # If it contains the word comedy then 1, else 0
  filter(is_comedy == 1 | genres == "Drama") %>% # Keep comedies and dramas
  mutate(genres = if_else(genres == "Drama", # Make it so that we only have those two genres
                          "Drama", 
                          "Comedy"))

glimpse(comedies_dramas) |>
  ggplot(aes(x = av_rating, group = genres, color = genres)) +
  geom_freqpoly() +
  labs(x = "Average Ratings", y = "Density", title = "Comedy vs. Drama")
```

I personally think that histograms are the most informative of the three plots.

## Question 6
