---
title: "DV (4) HW"
author: Carter Wyatt
format: html
editor: visual
embed resources: true
---

## Question 1

```{r}
library(tidyverse)

# Read in the data 
tv_ratings <- read_csv("https://raw.githubusercontent.com/vaiseys/dav-course/main/Data/tv_ratings.csv")

# Glimpse the data 
glimpse(tv_ratings)
```

```{r}
tv_long <- tv_ratings %>% 
  group_by(title) %>% 
  summarise(num_seasons = n()) %>% 
  ungroup() %>% 
  left_join(tv_ratings, by = "title") 

tv_long <- tv_long %>% 
  filter(num_seasons >= 5)
```

Use `tv_long` to make a line plot to trace how average ratings evolve across seasons. Remember to use the group aesthetic so that each line represents one show.

```{r}
tv_long |>
  ggplot(data = tv_long, mapping = aes(x = seasonNumber, y = av_rating, group = titleId)) + 
geom_line() +
  labs( x = "Seasons", y = "Average Ratings", title = "How Average Ratings Evolve Across Seasons")
```

It should look fairly messy. Can you draw any conclusions from it?

The only conclusions that I can draw is the average ratings seem to dip fairly low every five years and they are rising back to the top by season twenty.

## Question 2

```{r}
tv_long |>
  ggplot(data = tv_long, mapping = aes(x = seasonNumber, y = av_rating, group = titleId)) + 
geom_line() +
  labs( x = "Seasons", y = "Average Ratings", title = "How Average Ratings Evolve Across Seasons") +
  facet_wrap(~genres)
```

What shows tend to last longer?

It seems that crime, drama, and mystery seem to last as they span across the most amount of seasons.

Do ratings change much across seasons?

Ratings do change very much across seasons, the line is up and down continuously on the graph.

Can you identify that show on `Drama, Family, Fantasy` whose ratings just plummeted?

The show "Are You Afraid of the Dark?" caused the ratings to plummet.

## Question 3

```{r}
 tv_ratings |> 
  group_by(genres) |> 
  filter(av_rating >= 9) |> 
  ggplot(aes(x = genres)) +
  geom_bar() +
   coord_flip()

```

Tell me what `coord_flip()` does?

The function "coord_flip", completely flips the x and y variable so it is easier to read on the graph.

What is the genre with the most top-rated shows?

Drama is by far the genre with the most top-rated shows.

## Question 4

## Question 5

## Question 6
