---
title: "DV(1-3) HW"
author: "Carter Wyatt"
format: html
editor: visual
embed-resources: true
---

## Question 1

```{r}
library(tidyverse)
# Read in the data 
exercise_data <- read_csv("https://raw.githubusercontent.com/vaiseys/dav-course/main/Data/visualize_data.csv")
glimpse(exercise_data)
```

Before, we see examine anything from the data, write down what you expect the relationship would look like. Do you think people who record more exercise will have more or less BMI?

I expect the relationship to look like BMI will be directly affected by exercise. I think people who record more exercise will have less BMI.

Run the following code and tell me what the output indicates.

```{r}
cor(exercise_data$Exercise, exercise_data$BMI)

```

The output indicates that the BMI is directly affected and decreased by exercise.

Let's explore this relationship visually. Make a scatterplot with exercise in the x axis and BMI in the y axis.

```{r}
 exercise_data |>
   ggplot(aes(x = Exercise,
            y = BMI)) + geom_point()
```

## Question 2

```{r}
install.packages("causact")
```

```{r}
library(causact)
glimpse(corruptDF)
```

```{r}
?corruptDF
```

CPI2017 captures how corrupt a country is in the year 2017 from a scale from 0 which is the worst, and 100 which is the best.

HDI2017 captures how well-developed a country is compared to other countries in the year 2017 based on their longevity, education, and income.

## Question 3

```{r}
 exercise_data |>
   ggplot(aes(x = CPI2017,
            y = HDI2017)) + geom_point()
```

## Question 4

## Question 5

## Question 6

## Question 7

## Question 8
