---
title: "DV(1-3) HW"
author: "Carter Wyatt"
format: html
editor: visual
embed-resources: true
---

## Question 1

```{r}
library(tidyverse)
# Read in the data 
exercise_data <- read_csv("https://raw.githubusercontent.com/vaiseys/dav-course/main/Data/visualize_data.csv")
glimpse(exercise_data)
```

```{r}
## Rows: 142
## Columns: 4
## $ ...1     <dbl> 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18…
## $ ...2     <dbl> 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18…
## $ Exercise <dbl> 55.3846, 51.5385, 46.1538, 42.8205, 40.7692, 38.7179, 35.6410…
## $ BMI      <dbl> 1.8320590, 1.7892194, 1.7321050, 1.6178724, 1.5036362, 1.3751…
```

Before, we see examine anything from the data, write down what you expect the relationship would look like. Do you think people who record more exercise will have more or less BMI?

I expect the relationship to look like BMI will be directly affected by exercise. I think people who record more exercise will have less BMI.

Run the following code and tell me what the output indicates.

```{r}
cor(exercise_data$Exercise, exercise_data$BMI)

```

The output indicates that the BMI is directly affected and decreased by exercise.

Let's explore this relationship visually. Make a scatterplot with exercise in the x axis and BMI in the y axis.

```{r}
 exercise_data |>
   ggplot(aes(x = Exercise,
            y = BMI)) + geom_point()
```

## Question 2

## Question 3

## Question 4

## Question 5

## Question 6

## Question 7

## Question 8
