---
title: "HWDV6"
author: Carter Wyatt
format: html
editor: visual
embed-resources: true
---

```{r}
library(tidyverse)
# Set our ggplot theme from the outset
theme_set(theme_light())
# Read in the data 
gender_employment <- read_csv("https://raw.githubusercontent.com/vaiseys/dav-course/main/Data/gender_employment.csv")

# Glimpse at the data 
glimpse(gender_employment)
```

```{r}
gender_employment%>% 
  ggplot(aes(x = year, y = wage_percent_of_male)) +
  geom_jitter(alpha = 0.1) + 
  geom_smooth(method = "lm") + 
  labs(title = "Women's earnings with respect to men's", 
       y = "% of Men's Income", 
       x = "Year")
```

```{r}
library(broom)
```

```{r}
library(moderndive)
```

## Question 1

```{r}
gender_employment <- gender_employment %>% 
  mutate(major_category = as.factor(major_category), 
         major_category = relevel(major_category, ref = "Management, Business, and Financial"))
```

Let's begin by fitting a model where `wage_percent_of_male` is the outcome variable and the explanatory variables are `year` and `major_category`

DONE

```{r}
parallel_model <- lm(wage_percent_of_male ~ year + major_category, data = gender_employment)
broom::tidy(parallel_model)
```

Now, fit the model described above and save it as `parallel_model`. Using `tidy()` from the `broom` package, summarize the results. Can we say anything about overall trends by year?

The overall trends by year is substantially decreasing at a rate of -300.4 according to the data.

Okay, that was a lot. Now you do some interpretation.

Using the coefficients from your model, calculate the wage percentage of male income for Sales and Office occupations on 2015.

I am unsure.

Now calculate the wage percentage of male income for Service occupations on 2016.

I am unsure.

## Question 2

```{r}
gender_employment |>
  ggplot(aes(x = year, y = wage_percent_of_male, group = major_category, colour = major_category)) + geom_jitter(alpha = 0.5) + 
labs(title = "Women's earnings with respect to men's", 
       y = "% of Men's Income", 
       x = "Year") 
```

What do you notice? Is the parallel trends assumption warranted?

I notice that the parallel trends assumption is indeed warranted, and that using color to facet it makes this much easier to understand and interpret.

## Question 3

## Question 4

Given that we have the ability to add interactions to models - i.e. to have slopes vary across categories -, why would we choose to build a model that assumes parallel trends?

We would choose to build a model that assumes parallel trends because it allows for the data to be more descriptive and constant.

## Question 5

## Question 6
