---
title: "MD HW5"
author: "Carter Wyatt"
format: html
editor: visual
embed resources: true
---

```{r}
library(tidyverse)


twitch_data <- read_csv("https://raw.githubusercontent.com/vaiseys/dav-course/main/Data/twitchdata-update.csv")
```

```{r}
library(janitor)
twitch_data <- clean_names(twitch_data)

# Inspect new names
colnames(twitch_data)
```

## Question 1

```{r}

twitch_data |>
  select(channel, average_viewers, followers) |>
  sample_n(size = 5) 

```

What do you notice?

```{r}
twitch_data |>
  select(channel, average_viewers, followers) |>
  sample_n(size = 5) |>
summarise(average_viewers, followers)
```

Describe the results in a few words. Does anything capture your attention?

```{r}
twitch_data |>
  select(channel, average_viewers, followers) |>
  sample_n(size = 5) |>
summarise(average_viewers, followers) |>
  ggplot(
    aes(x = average_viewers, y = followers)
  ) +
  geom_point() +
  labs(x = "Average Viewers", y = "Followers", title = "Random Channels")
```

What do you notice?

```{r}
twitch_data |>
  select(channel, average_viewers, followers) |>
  sample_n(size = 5) |>
summarise(average_viewers, followers) |>
  ggplot(
    aes(x = average_viewers, y = followers)
  ) +
  geom_point() +
  labs(x = "Average Viewers", y = "Followers", title = "Random Channels") +
  scale_x_log10() + scale_y_log10()
```

What do you see now? How does the relationship look like?

```{r}
twitch_data <- twitch_data %>% 
  mutate(log_viewers = log10(average_viewers), 
         log_followers = log10(followers))
```

## Question 2

```{r}

fit1 <- lm(log_viewers ~ log_followers,  data = twitch_data) 
```

\$\$ 1.1\^{0.4} = 4.442731 \$\$

A 10% increase in followers is associated with a 4.2% increase in the average number of viewers.

## Question 3

```{r}
library(broom)

pred_data <- augment(fit1)

# glimpse our new data 
glimpse(pred_data)
```

```{r}
pred_data %>% 
  ggplot(aes(x = log_followers, 
             y = log_viewers)) +
  geom_jitter(alpha = 0.4) + 
  geom_line(aes(x = log_followers, 
                y = .fitted), 
            col = "orange") + 
  theme_minimal() +
  labs(subtitle = "Fitted Model and Raw Data", 
       title = "Followers & Average Viewership", 
       x = "log(followers)", 
       y = "log(viewers)")
```

Do you think our model describes the relationship well?

```{r}
pred_data %>% 
  ggplot(aes(x = log_followers, 
             y = .resid)) +
  geom_jitter(alpha = 0.4) + 
  geom_line(aes(x = log_followers, 
                y = .fitted), 
            col = "orange") + 
  theme_minimal() +
  labs(subtitle = "Fitted Model and Raw Data", 
       title = "Followers & Average Viewership", 
       x = "log(followers)", 
       y = "log(viewers)")
```

What do you see? Are there any big residuals? DO they happen often in a particular range of our x-variable? If so, we would have a problem: our model would systematically fail to predict part of our data.

## Question 4

1.  The raw data

2.  Summaries of the variables

```{r}
fit2 <- lm(log_viewers ~ language, data = twitch_data)
```

1.  Plot the variables

```{r}
twitch_data |>
  ggplot(
    aes(x = average_viewers)) +   geom_boxplot() + facet_wrap(~language) +
  labs(x = "Total Number", y = "Average Viewers", title = "Language Average Views")
```

## Question 5

```{r}
fit3 <- lm(average_viewers ~ language, data = twitch_data)
```

```{r}
twitch_data <- twitch_data %>% 
  mutate(language = as.factor(language), 
         language = relevel(language, ref = "English"))
```

```{r}
twitch_data |> ggplot(aes(x = average_viewers, y = language)) + geom_jitter(alpha = 0.4) + geom_line(aes(x = average_viewers, y = language), col = "red") + theme_minimal()
```

Now, fit your model. Your coefficients will tell you how many more (or fewer) average viewers are related to streaming in languages different than English. Interpret the results. How is my prediction doing?

## Question 6

Explore the residuals here using a similar plot as above. There are a couple of points our model really missed - which ones were they?
